---
title: "IPV Terms Analysis"
author: "Bryan Victor"
date: "Tuesday, January 27, 2015"
output: pdf_document
---

Databases used: Anthropoligical Literature, CINAHL, Education Abstracts, ERIC, Humanities & Social Sciences Index Retrospective: 1907-1984, MEDLINE, PsycARTICLES, PsycINFO, and Social Work Abstracts

Search term: "domestic violence" or "intimate partner violence" or "battering" or "family violence" or "wife abuse" or "partner abuse" or "spouse abuse" or "dating violence" or "relationship violence"

Original article count: 11,897



```{r, echo=FALSE, comment=NA}
library(dplyr)
library(ggplot2)

setwd("C:/Users/Tom/Documents/GitHub/IPVTerms")

load("titlesearch_df.R") #titles.df
load("titlesearch_shorttitles.R") #titles.shorttitles

IPV.years<-titles.df%>%
  filter(attributes =="YR")%>%
  select(-attributes, articleID, Year=record)

titles<-merge(titles.shorttitles, IPV.years, by="articleID")
titles$Year<-as.character(titles$Year)
titles$Year<-as.numeric(titles$Year)

#DOMESTIC VIOLENCE

DV.set<-filter(titles, grepl("domestic violence", short.title, ignore.case=T))
DV.set<-filter(DV.set, Year<2014)

n.DV.year <- DV.set %>% 
  group_by(Year) %>%
  summarise(n = n())

n.DV.year<-select(n.DV.year, Year, DV=n)

#INTIMATE PARTNER VIOLENCE

IPV.set<-filter(titles, grepl("intimate\\spartner\\sviolence", short.title, ignore.case=T))
IPV.set<-filter(IPV.set, Year<2014)

n.IPV.year <- IPV.set %>% 
  group_by(Year) %>%
  summarise(n = n())

n.IPV.year<-select(n.IPV.year, Year, IPV=n)

#FAMILY VIOLENCE

FV.set<-filter(titles, grepl("family\\sviolence", short.title, ignore.case=T))
FV.set<-filter(FV.set, Year<2014)

n.FV.year <- FV.set %>% 
  group_by(Year) %>%
  summarise(n = n())

n.FV.year<-select(n.FV.year, Year, FV=n)

#BATTERING

BAT.set<-filter(titles, grepl("battering", short.title, ignore.case=T))
BAT.set<-filter(BAT.set, Year<2014)

n.BAT.year <- BAT.set %>% 
  group_by(Year) %>%
  summarise(n = n())

n.BAT.year<-select(n.BAT.year, Year, BAT=n)

#WIFE ABUSE

WA.set<-filter(titles, grepl("wife\\sabuse", short.title, ignore.case=T))
WA.set<-filter(WA.set, Year<2014)

n.WA.year <- WA.set %>% 
  group_by(Year) %>%
  summarise(n = n())

n.WA.year<-select(n.WA.year, Year, WA=n)

#SPOUSE ABUSE

SA.set<-filter(titles, grepl("spouse\\sabuse", short.title, ignore.case=T))
SA.set<-filter(SA.set, Year<2014)

n.SA.year <- SA.set %>% 
  group_by(Year) %>%
  summarise(n = n())

n.SA.year<-select(n.SA.year, Year, SA=n)

#PARTNER ABUSE

PA.set<-filter(titles, grepl("partner\\sabuse", short.title, ignore.case=T))
PA.set<-filter(PA.set, Year<2014)

n.PA.year <- PA.set %>% 
  group_by(Year) %>%
  summarise(n = n())

n.PA.year<-select(n.PA.year, Year, PA=n)

#DATING VIOLENCE

DATING.set<-filter(titles, grepl("dating\\sviolence", short.title, ignore.case=T))
DATING.set<-filter(DATING.set, Year<2014)

n.DATING.year <- DATING.set %>% 
  group_by(Year) %>%
  summarise(n = n())

n.DATING.year<-select(n.DATING.year, Year, DATING=n)

#RELATIONSHIP VIOLENCE

REL.set<-filter(titles, grepl("relationship\\sviolence", short.title, ignore.case=T))
REL.set<-filter(REL.set, Year<2014)

n.REL.year <- REL.set %>% 
  group_by(Year) %>%
  summarise(n = n())

n.REL.year<-select(n.REL.year, Year, REL=n)

#MERGER

merged<-merge(n.DV.year, n.IPV.year, by="Year", all=TRUE)
merged<-merge(merged, n.BAT.year, by="Year", all=TRUE)
merged<-merge(merged, n.FV.year, by="Year", all=TRUE)
merged<-merge(merged, n.WA.year, by="Year", all=TRUE)
merged<-merge(merged, n.SA.year, by="Year", all=TRUE)
merged<-merge(merged, n.PA.year, by="Year", all=TRUE)
merged<-merge(merged, n.DATING.year, by="Year", all=TRUE)
merged<-merge(merged, n.REL.year, by="Year", all=TRUE)
merged[is.na(merged)] <- 0

term.count <- ggplot(merged, aes(as.numeric(Year), y=n, group=1, color=Terms)) + 
  geom_line(aes(y = DV, colour="Domestic Violence")) +
  geom_line(aes(y = IPV, colour="Intimate Partner Violence")) + 
  geom_line(aes(y = BAT, colour="Battering"))+
  geom_line(aes(y = FV, colour="Family Violence"))+
  geom_line(aes(y = WA, colour="Wife Abuse"))+
  geom_line(aes(y = SA, colour="Spouse Abuse"))+
  geom_line(aes(y = PA, colour="Partner Abuse"))+
  geom_line(aes(y = DATING, colour="Dating Violence"))+
  geom_line(aes(y = REL, colour="Relationship Violence"))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("Year") + 
  ylab("Frequency") + 
  ggtitle("") + 
  scale_x_continuous(breaks=seq(1963, 2013, 10))

print(term.count)

```

#Stacked Bar Chart - Titles

```{r}

library(reshape2)

colnames(merged)<-c("Year", "domestic violence", "intimate partner violence", "battering", 
                    "family violence", "wife abuse", "spouse abuse", "partner abuse", 
                    "dating violence", "relationship violence")

meltedmerge<-melt(merged, id.vars = "Year")

colnames(meltedmerge)<-c("Year", "Term", "Frequency")

ggplot(meltedmerge, aes(x = Year, y = Frequency, fill=Term)) +
       geom_bar(stat="identity") 

                                                                                    


```

#Journal Analysis by title search

```{r}

n.so.yr <- filter(titles.df, attributes == "SO" | attributes == "YR")

n.so <- filter(titles.df, attributes == "SO") %>% mutate(title = record) %>% 
        select(-attributes, -record)

n.yr <- filter(titles.df, attributes == "YR") %>% mutate(year = record ) %>% 
        select(-attributes, -record)

n.yr<-filter(n.yr, year<=2013)

n.so.yr <- merge(n.yr, n.so) %>%
    group_by(title) %>%
    summarise(first = min(year), last = max(year), n.to.date = n()) %>%
    arrange(desc(n.to.date))

# 10 highest number of publications
head(n.so.yr, 15)

```


#Keyword Analysis

```{r}
load("keywordsearch_df.R")
terms <- KW.df %>%
  filter(attributes=="KP")

years<-KW.df %>%
  filter(attributes=="YR")%>%
  select(articleID, year=record)

years$year<-as.character(years$year)
years$year<-as.numeric(years$year)

merged<-merge(terms, years, by="articleID")
merged<-select(merged, keyword=record, year)

#DOMESTIC VIOLENCE

DV.set<-filter(merged, grepl("domestic violence|Domestic Violence", keyword))
DV.set<-filter(DV.set, year<2014)

n.DV.year <- DV.set %>% 
  group_by(year) %>%
  summarise(n = n())

n.DV.year<-select(n.DV.year, year, DV=n)

#INTIMATE PARTNER VIOLENCE

IPV.set<-filter(merged, grepl("intimate partner violence|Intimate Partner Violence", keyword))
IPV.set<-filter(IPV.set, year<2014)

n.IPV.year <- IPV.set %>% 
  group_by(year) %>%
  summarise(n = n())

n.IPV.year<-select(n.IPV.year, year, IPV=n)

#FAMILY VIOLENCE

FV.set<-filter(merged, grepl("family violence|Family Violence", keyword))
FV.set<-filter(FV.set, year<2014)

n.FV.year <- FV.set %>% 
  group_by(year) %>%
  summarise(n = n())

n.FV.year<-select(n.FV.year, year, FV=n)

#BATTERING

BAT.set<-filter(merged, grepl("batter|Batter", keyword))
BAT.set<-filter(BAT.set, year<2014)

n.BAT.year <- BAT.set %>% 
  group_by(year) %>%
  summarise(n = n())

n.BAT.year<-select(n.BAT.year, year, BAT=n)

#WIFE ABUSE

WA.set<-filter(merged, grepl("wife abuse|Wife Abuse", keyword))
WA.set<-filter(WA.set, year<2014)

n.WA.year <- WA.set %>% 
  group_by(year) %>%
  summarise(n = n())

n.WA.year<-select(n.WA.year, year, WA=n)

#SPOUSE ABUSE

SA.set<-filter(merged, grepl("spouse abuse|Spouse Abuse", keyword))
SA.set<-filter(SA.set, year<2014)

n.SA.year <- SA.set %>% 
  group_by(year) %>%
  summarise(n = n())

n.SA.year<-select(n.SA.year, year, SA=n)

#PARTNER ABUSE

PA.set<-filter(merged, grepl("partner abuse|Partner Abuse", keyword))
PA.set<-filter(PA.set, year<2014)

n.PA.year <- PA.set %>% 
  group_by(year) %>%
  summarise(n = n())

n.PA.year<-select(n.PA.year, year, PA=n)

#DATING VIOLENCE

DATING.set<-filter(merged, grepl("dating violence|Dating Violence", keyword))
DATING.set<-filter(DATING.set, year<2014)

n.DATING.year <- SA.set %>% 
  group_by(year) %>%
  summarise(n = n())

n.DATING.year<-select(n.DATING.year, year, DATING=n)

#RELATIONSHIP VIOLENCE

REL.set<-filter(merged, grepl("relationship violence|Relationship Violence", keyword))
REL.set<-filter(REL.set, year<2014)

n.REL.year <- SA.set %>% 
  group_by(year) %>%
  summarise(n = n())

n.REL.year<-select(n.REL.year, year, REL=n)

KW<-merge(n.DV.year, n.IPV.year, by="year", all=TRUE)
KW<-merge(KW, n.BAT.year, by="year", all=TRUE)
KW<-merge(KW, n.FV.year, by="year", all=TRUE)
KW<-merge(KW, n.WA.year, by="year", all=TRUE)
KW<-merge(KW, n.SA.year, by="year", all=TRUE)
KW<-merge(KW, n.PA.year, by="year", all=TRUE)
KW<-merge(KW, n.DATING.year, by="year", all=TRUE)
KW<-merge(KW, n.REL.year, by="year", all=TRUE)
KW[is.na(KW)] <- 0

KW.count <- ggplot(KW, aes(as.numeric(year), y=n, group=1, color=Keywords)) + 
  geom_line(aes(y = DV, colour="Domestic Violence")) +
  geom_line(aes(y = IPV, colour="Intimate Partner Violence")) + 
  geom_line(aes(y = BAT, colour="Battered/Battering"))+
  geom_line(aes(y = FV, colour="Family Violence"))+
  geom_line(aes(y = WA, colour="Wife Abuse"))+
  geom_line(aes(y = SA, colour="Spouse Abuse"))+
  geom_line(aes(y = PA, colour="Partner Abuse"))+
  geom_line(aes(y = DATING, colour="Dating Violence"))+
  geom_line(aes(y = REL, colour="Relationship Violence"))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("Year") + 
  ylab("Frequency") + 
  ggtitle("") + 
  scale_x_continuous(breaks=seq(1963, 2013, 10))

print(KW.count)
```


#Journal Analysis by keyword search

```{r}

n.so.yr <- filter(KW.df, attributes == "SO" | attributes == "YR")

n.so <- filter(KW.df, attributes == "SO") %>% mutate(title = record) %>% 
        select(-attributes, -record)

n.yr <- filter(KW.df, attributes == "YR") %>% mutate(year = record ) %>% 
        select(-attributes, -record)

n.yr<-filter(n.yr, year<=2013)

n.so.yr <- merge(n.yr, n.so) %>%
    group_by(title) %>%
    summarise(first = min(year), last = max(year), n.to.date = n()) %>%
    arrange(desc(n.to.date))

# 15 highest number of publications
head(n.so.yr, 15)

```


#Google Trend Data 

```{r, echo=FALSE, comment=NA, message=FALSE}

google<-read.csv("googletrend.csv")
google$Week<-strtrim(google$Week, 10)
google<-google[1:522,]
google$Week<-as.Date(google$Week)
google$domestic.violence<-as.numeric(google$domestic.violence)

google.count <- ggplot(google, aes(x=Week)) + 
  geom_line(aes(y = domestic.violence, colour="domestic violence")) +
  geom_line(aes(y = intimate.partner.violence, colour="intimate partner violence")) + 
  geom_line(aes(y = dating.violence, colour="dating violence"))+
  geom_line(aes(y = family.violence, colour="family violence"))+ scale_x_date() + 
  xlab("Year") + 
  ylab("Google Popularity Rating")

google.count<- google.count + scale_color_discrete(name="Google Search Terms")

print(google.count)

```

